\documentclass[letterpaper,11pt,oneside]{article}
\pagestyle{empty}
\usepackage{array}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{microtype}

% Font configuration
\renewcommand*\familydefault{\sfdefault}
\renewcommand*\sfdefault{phv} % Default font: Helvetica
\DisableLigatures{encoding = *, family = *}

% Margin and spacing configuration
\raggedbottom
\raggedright
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

\setlist[itemize]{parsep=0pt, topsep=4pt}
\setlist[description]{parsep=0pt, topsep=4pt}

% Display name, e-mail, and phone number at the top of the page
% Currently uses Avant Garde font
\newcommand{\mkheader}[3]{
  {\fontfamily{pag}\selectfont
  \begin{tabularx}{\textwidth}{lXr}
    \multirow{2}{*}{\Huge #1} && \emph{#2}
    \\ && \emph{#3}
    % \\ \hline
  \end{tabularx}
  }
  \vspace{2pt}
  \hrule
}

% Mark section with larger font
\newcommand{\resheader}[2][]{
  \vspace{9pt}
  {\LARGE #2} #1
  \\
}

\newcommand{\ressubheader}[3][]{
  \vspace{6pt}
  {\large \textbf{#2} #1} \hfill \emph{#3}
  \\
}

% Emphasize skill in text block
\newcommand{\resskill}[1]{\textbf{#1}}

\begin{document}
\mkheader{William Cromar}{wcromar@knights.ucf.edu}{904-814-9428}

\resheader{Skills and Technologies}
\vspace{6pt}
\begin{tabular}{>{\bfseries}l@{\hskip .25cm} l}
  Languages: & Java, Python, C, C++, Octave, SQL, HTML/CSS, LaTeX \\
  Operating Systems: & Linux (including Bash command line), Windows 7/8/10 \\
  Development Tools: & iPython, Git, Subversion (SVN), MS Visual Studio, CMake \\
  Libraries: & Scikit-Learn, TensorFlow, NumPy, NLTK, Seaborn
\end{tabular}


\resheader{Education}
\ressubheader{University of Central Florida}{Fall 2015 - Spring 2019 (expected)}
Bachelor of Science, Computer Science \hfill \emph{Current GPA 3.88} \\
Burnett Honors College

\ressubheader{St. Johns River State College}{Fall 2013 - Spring 2015}
Computer Programming and Analysis \hfill \emph{Final GPA: 3.9} \\

\resheader{Experience}
\ressubheader[(UCF)]{Member, JV Programming Team}{September 2016 - Present}
\begin{itemize}
  \item Attend weekly practice competitions to improve problem solving skills
    and programming ability. Implement efficient software solutions in
    \resskill{Java} within a short timeframe. 
  \item Collaborate and communicate with other team members to design and
    implement creative solutions to challenging problems. Test solutions to
    ensure correctness.
\end{itemize}

\ressubheader[(DiSTI)]{Software Engineer Intern}{October 2015 - September 2016}
\begin{itemize}
  \item Developed and maintained leading-edge virtual environment software
    written in \resskill{C++}. Identified, reported, and resolved bugs in a
    large code-base.
    \item Tested software solutions and reviewed code written by team members to
      ensure consistent software quality. Created and improved automated tests
      using in-house tools and, as well as custom \resskill{Python} scripts.
\end{itemize}

\resheader[\hfill \texttt{github.com/will-cromar}]{Projects}
\begin{description}
  \item [Sentiment Classifier:] Developed a natural language
    sentiment classifier in \resskill{Python} using \resskill{sklearn}, capable
    of identifying positive or negative tone in bodies of text. Trained using
    real-world natural language data, preprocessed with \resskill{NLTK}.
    Incorporated sentiment classifier into larger group project providing stock
    market news analysis, price prediction, and report generation.
  \item [Connect-4 AI:] Implemented an automated \emph{Connect-4} player from
    scratch in \resskill{C}. Incorporates probabalistic methods such as
    Monte-Carlo Search Trees, as well as heuristic techniques from game theory
    to efficiently achieve near-optimal play.
  \item [PL/0 Compiler:] Collaborated with a team of two other people to
    implement, in \resskill{C}, a compiler for the PL/0 programming language.
    Capable of lexing, parsing, and generating bytecode for PL/0 source files.
    Implemented virtual machine to test generated bytecode.
  \item [Text Editor:] Developed a basic graphical plain-text editor in
    \resskill{Java} using the \resskill{Swing} framework, capable of reading and
    writing to text files. Constructed UML class diagram to document object
    relationships.
\end{description}    
% \ressubheader{Sentiment Classifier}{Fall 2015}
% \begin{itemize}
%   \item Developed a natural language sentiment classifier in \resskill{Python}
%     using \resskill{sklearn}, capable of identifying positive or negative tone
%     in bodies of text.
%   \item Trained using real-world natural language data, preprocessed with
%     \resskill{NLTK}.
%   \item Incorporated sentiment classifier into larger group project providing
%     stock market news analysis, price prediction, and report generation.
% \end{itemize}

% \ressubheader{Connect-4 AI}{Spring 2016}
% \begin{itemize}
%   \item Implemented an automated \emph{Connect-4} player from scratch in
%     \resskill{C}.
%   \item Incorporates probabalistic methods such as Monte-Carlo Search Trees,
%     as well as heuristic techniques from game theory to efficiently achieve
%     near-optimal play.
% \end{itemize}

% \ressubheader{PL/0 Compiler}{Fall 2016}
% \begin{itemize}
%   \item Collaborated with a team of three people to design and
%     implement a VM, lexer, parser, and compiler for the programming language
%     PL/0.
% \end{itemize}


\end{document}